\chapter{Conclusions}

\section{Contributions}
This work has implemented a prototype hardware, tested current sensing with a
free-field sensor, discovered issues with interconnect fragility, identified a
path forward for controls development.

\section{Future Work}

\subsection{Multi-phase IMMD}
While the one phase per controller drive shown here provides significant gains
in redundancy, multi-phase per controller modular designs show promise for
simplifying the control of very large machines by allowing reduced converter
complexity and wider application of commodity power switching components.
Furthermore, having multiple phase voltages controlled by one controller
significantly reduces the communications and coordination overhead in the
system.


\subsection{EMI analysis}
Further work on EMI analysis is needed both in emission and susceptibility for
tightly integrated motors and drives.
This prototype implemented a few rules of thumb to allow the drive to operate,
but there may be significant possible savings in weight and volume if the
large baseplate can be eliminated.
Furthermore, the savings in shielded cabling allowed by no longer having long
motor phase leads with large dV/dt waveforms may make tightly integrated
drives attractive to many applications.

\subsection{Control Development}
This work did not succeed in implementing high-bandwidth vector control.
The most significant challenge is managing sensor tolerances in order to have
all phases share power handling equally as independent controllers are not
inherently symmetrical and can easily turn sensor errors into negative
sequence components in the machine currents.

\subsection{High-temperature Testing}
This controller design was chosen with high temperature coolant in mind as
multiple coolant loops are a significant overhead in current hybrid and
electric vehicle designs.
This design should be run at high temperature to determine where the actual
thermal bottlenecks are so future designs can allow shared coolant between
the drive and other system components.
